An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{JMC, BB and HS were supported by NIH grant 5R01EY025332 and NIDILRR grant 90RE5024-01-00. We thank Dr. Roberto Manduchi, Dr. Natela Shanidze, Dr. Santani Teng and Dr. Ali Cheraghi for helpful suggestions about the experiments.}

### 2020-06-09 manuscript.tex
Update tex

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{Thank you for ...}}
\titlerunning{Audio-Based 3D Spatial Guidance}

\author{James Coughlan\inst{1}\orcidID{0000-0003-2775-4083} \and
Brandon Biggs\inst{1} \and
Marc-Aurèle Rivière\inst{2}\orcidID{0000-0002-5108-3382} \and
Huiying Shen\inst{1}}

\authorrunning{J. Coughlan et al.}

@@

\keywords{Assisitive Devices
\and Augmented Reality
\and Auditory Substitution
\and Visual Impairment}
\end{abstract}
%

@@

CamIO is an augmented reality (AR) iPhone app that uses computer vision
to provide audio labels for rigid 3D objects. The rigid object of
interest is mounted on a board, which is a printed barcode pattern
(\ref{fig:exp}) that allows CamIO to estimate the object's pose (3D
translation and 3D orientation) relative to the camera. The iPhone is
typically mounted on a tripod or a gooseneck cellphone holder
\ref{fig:exp} to obtain a clear view of the board and object, but in
some cases \cite{coughlanTowardsAccessibleAudioLabeling2020} users may
hold the iPhone by hand. The user points the tip of a passive wooden
stylus \ref{fig:exp}, covered with another barcode pattern, to different
locations on an object. CamIO estimates the stylus tip's 3D location
relative to the camera and uses the pose estimate of the board to
determine the stylus tip's 3D location relative to the object. Whenever
the tip is close enough to a pre-defined hotspot, it triggers audio
information about the hotspot. (In other words, hotspot locations are
defined relative to the board, which is mounted rigidly to the object.)

A second stylus (not shown, identical in form but distinct from the one
shown in \ref{fig:exp}) is used to create new hotspots, and allows the
user to make an audio recording to associate with each new hotspot. Our
recent work \cite{coughlanTowardsAccessibleAudioLabeling2020}
demonstrates the accessibility of this authoring process, which allows
blind users to create their own annotations (hotspots and associated
audio labels) independently. However, in the study presented in this
paper, the experimenter was the only one who created hotspots, since the
emphasis here is on providing guidance to pre-existing hotspots.

@@

We define the guidance interface as follows. The board (barcode pattern
beneath the truck, see \ref{fig:exp}) defines an xyz coordinate frame,
with \(+x\) = right, \(-x\) = left, \(+y\) = forward (away from the
user), \(-y\) = back (towards the user), \(+z\) = up and \(-z\) = down.
Let the desired target hotspot location be denoted \((x*, y*, z*)\), and
the current location of the stylus tip be \((x,y,z)\). Define the error
vector \(e = (x-x*, y-y*, z-z*)\), and let index \(a = argmax_i |e_i|\),
i.e., a is the index (1, 2 or 3, corresponding to x, y or z,
respectively) of the entry in e with the highest absolute value. In
other words, a indicates which coordinate (x, y or z) is most discrepant
from the target coordinate location \((x*, y*, z*)\). Then the
appropriate direction is issued, e.g., ``left'' if \(a = 1\) and
\(x > x*\), ``right'' if \(a = 1\) and \(x < x*\), ``up'' if \(a = 3\)
and \(z < z*\), etc. Directions are announced roughly twice per second
whenever the stylus is visible. The target hotspot is announced when the
stylus gets to within approximately 1 cm from the hotspot. No audio
feedback is issued when the stylus is not visible.

@@

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment \ref{fig:exp} compared how much time a
blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (\ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

@@

Each hotspot location was searched for under two feedback conditions: G
(guidance provided) and NG (no guidance). The participant was given up
to 120 sec.~to find each hotspot, after which a time-out was declared.
In order to minimize the influence of any possible learning effects,
which could make it easier to find a hotspot the second time it was
searched for, we randomized the sequence of hotspots and alternated
between NG and G trials. This resulted in a sequence of 2K = 20 trials,
starting with an NG trial, the same sequence for each participant.

We had a total of N=4 blind participants in our experiment (2 male/2
female, ages from 26-42). Participants P1, P3 and P4 were already
familiar with the CamIO system (P4 is a co-author of this paper) while
P2 was unfamiliar with it. None of the participants was told the study
design before their trials, and we didn't tell them whether or not any
locations would be repeated in the 20 trials. After obtaining IRB
consent, we reviewed how CamIO works if necessary and demonstrated the
audio guidance feature. The experimenter launched CamIO on an iPhone 8
and positioned it on a gooseneck cellphone holder so that the camera
captured the entire truck and board. Each participant spent a short time
practicing with the guidance feature, with help provided by the
experimenter as needed. (The experimenter chose practice hotspots that
were different from the pre-defined K=10 hotspots.) In the practice
phase, the experimenter explained that barriers sometimes block the user
from moving in the suggested guidance direction. For instance, if in
\ref{fig:exp} the system directs the participant to move ``forward''
towards the left side mirror, the stylus will soon hit the cabin
roof/wall as it moves towards the mirror; the participant must find ways
around such obstacles to find the target hotspot.

Next each participant performed the formal experimental trials, which
consisted of the 2K=20 trial sequence described above. This sequence
included 10 trials of both conditions (G and NG), for a total of 20
trials per participant. After completing the 20 search trials, we
administered a System Usability Scale (SUS) \cite{brooke1996sus} to
estimate the usability of the guidance system. Finally, we conducted a
semi-structured interview asking what participants liked and disliked
about the system, what needed to be improved, and how they might
envision an ideal guidance system. Since P4 is a co-author on this
paper, we did not administer the SUS or semi-structured interview to
him.

@@

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment (\ref{fig:exp}) compared how much time a
blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (\ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

>>>>

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{JMC, BB and HS were supported by NIH grant 5R01EY025332 and NIDILRR grant 90RE5024-01-00. We thank Dr. Roberto Manduchi, Dr. Natela Shanidze, Dr. Santani Teng and Dr. Ali Cheraghi for helpful suggestions about the experiments.}}

\titlerunning{Audio-Based 3D Spatial Guidance}

\author{James M. Coughlan\inst{1}\orcidID{0000-0003-2775-4083} \and
Brandon Biggs\inst{1}\orcidID{0000-0001-7380-1077} \and
Marc-Aurèle Rivière\inst{2}\orcidID{0000-0002-5108-3382} \and
Huiying Shen\inst{1}\orcidID{0000-0002-2195-7085}}

\authorrunning{J. M. Coughlan et al.}

@@

\keywords{Assistive Devices
\and Accessibility
\and Augmented Reality
\and Auditory Substitution
\and Visual Impairment
\and Blindness
\and Low Vision}
\end{abstract}
%

@@

CamIO is an augmented reality (AR) iPhone app that uses computer vision
to provide audio labels for rigid 3D objects. The rigid object of
interest is mounted on a board, which is a printed barcode pattern
(Fig. \ref{fig:exp}) that allows CamIO to estimate the object's pose (3D
translation and 3D orientation) relative to the camera. The iPhone is
typically mounted on a tripod or a gooseneck cellphone holder
Fig. ref{fig:exp} to obtain a clear view of the board and object, but in
some cases \cite{coughlanTowardsAccessibleAudioLabeling2020} users may
hold the iPhone by hand. The user points the tip of a passive wooden
stylus Fig. \ref{fig:exp}, covered with another barcode pattern, to different
locations on an object. CamIO estimates the stylus tip's 3D location
relative to the camera and uses the pose estimate of the board to
determine the stylus tip's 3D location relative to the object. Whenever
the tip is close enough to a pre-defined hotspot, it triggers audio
information about the hotspot. (In other words, hotspot locations are
defined relative to the board, which is mounted rigidly to the object.)

A second stylus (not shown, identical in form but distinct from the one
shown in Fig. \ref{fig:exp}) is used to create new hotspots, and allows the
user to make an audio recording to associate with each new hotspot. Our
recent work \cite{coughlanTowardsAccessibleAudioLabeling2020}
demonstrates the accessibility of this authoring process, which allows
blind users to create their own annotations (hotspots and associated
audio labels) independently. However, in the study presented in this
paper, the experimenter was the only one who created hotspots, since the
emphasis here is on providing guidance to pre-existing hotspots.

@@

We define the guidance interface as follows. The board (barcode pattern
beneath the truck, see Fig. \ref{fig:exp}) defines an xyz coordinate frame,
with \(+x\) = right, \(-x\) = left, \(+y\) = forward (away from the
user), \(-y\) = back (towards the user), \(+z\) = up and \(-z\) = down.
Let the desired target hotspot location be denoted \((x*, y*, z*)\), and
the current location of the stylus tip be \((x,y,z)\). Define the error
vector \(e = (x-x*, y-y*, z-z*)\), and let index \(a = argmax_i |e_i|\),
i.e., a is the index (1, 2 or 3, corresponding to x, y or z,
respectively) of the entry in e with the highest absolute value. In
other words, a indicates which coordinate (x, y or z) is most discrepant
from the target coordinate location \((x*, y*, z*)\). Then the
appropriate direction is issued, e.g., ``left'' if \(a = 1\) and
\(x > x*\), ``right'' if \(a = 1\) and \(x < x*\), ``up'' if \(a = 3\)
and \(z < z*\), etc. Directions are announced roughly twice per second
whenever the stylus is visible. The target hotspot is announced when the
stylus gets to within approximately 1 cm from the hotspot. No audio
feedback is issued when the stylus is not visible.

@@

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment Fig. \ref{fig:exp} compared how much time a blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (Fig. \ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

@@

Each hotspot location was searched for under two feedback conditions: G
(guidance provided) and NG (no guidance). The participant was given up
to 120 sec to find each hotspot, after which a time-out was declared.
In order to minimize the influence of any possible learning effects,
which could make it easier to find a hotspot the second time it was
searched for, we randomized the sequence of hotspots and alternated
between NG and G trials. This resulted in a sequence of 2K = 20 trials,
starting with an NG trial, the same sequence for each participant.

We had a total of N=4 blind participants in our experiment (2 male/2
female, ages from 26-42). Participants P1, P3 and P4 were already
familiar with the CamIO system (P4 is a co-author of this paper) while
P2 was unfamiliar with it. None of the participants was told the study
design before their trials, and we didn't tell them whether or not any
locations would be repeated in the 20 trials. After obtaining IRB
consent, we reviewed how CamIO works if necessary and demonstrated the
audio guidance feature. The experimenter launched CamIO on an iPhone 8
and positioned it on a gooseneck cellphone holder so that the camera
captured the entire truck and board. Each participant spent a short time
practicing with the guidance feature, with help provided by the
experimenter as needed. (The experimenter chose practice hotspots that
were different from the pre-defined K=10 hotspots.) In the practice
phase, the experimenter explained that barriers sometimes block the user
from moving in the suggested guidance direction. For instance, if in
Fig. \ref{fig:exp} the system directs the participant to move ``forward''
towards the left side mirror, the stylus will soon hit the cabin
roof/wall as it moves towards the mirror; the participant must find ways
around such obstacles to find the target hotspot.

Next each participant performed the formal experimental trials, which
consisted of the 2K=20 trial sequence described above. This sequence
included 10 trials of both conditions (G and NG), for a total of 20
trials per participant. We  placed a visual barrier between the participant and the object while the experimenter defined the hotspot in each trial to prevent participants from using any residual vision to see the location of the hotspot. After completing the 20 search trials, we
administered a System Usability Scale (SUS) \cite{brooke1996sus} to
estimate the usability of the guidance system. Finally, we conducted a
semi-structured interview asking what participants liked and disliked
about the system, what needed to be improved, and how they might
envision an ideal guidance system. Since P4 is a co-author on this
paper, we did not administer the SUS or semi-structured interview to
him.

@@

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment (Fig. \ref{fig:exp}) compared how much time a
blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (Fig. \ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.
